%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-Stack Engineer Intern} % Job title
    {Shop Bonsai} % Organization
    {Toronto} % Location
    {May. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Techstack: TypeScript, Node.js, Apollo, GraphQL, React.js, MongoDB}
        \item {Added features to internal dashboard including product filters, and a user management system for administrators.}
        \item {Created external order fulfillment system for use by the Customer Experience team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer Intern} % Job title
    {Shop Bonsai} % Organization
    {Toronto} % Location
    {Jan. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Techstack: Bash, Terraform, Docker, Kubernetes, Google Cloud, CI/CD, TypeScript, Node.js, Express.js}
        \item {Implemented infrastructure as code using Terraform, automating Google Cloud deployments and MongoDB cluster creation.}
        \item {Improved monorepo by transitioning to Yarn V2 with local caching speeding up deployment and CI/CD workflows by 18 minutes.}
        \item {Revamped Express image API written in TypeScript by decoupling upload/download and splitting into micro-services.}
        \item {Optimized Docker build size by over 90\% by implementing multistage builds and parent images.}
        \item {Enforced best practices with linting and E2E tests through GitHub Actions and Semaphore CI.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
