%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director of Technology} % Affiliation/role
    {Limestone Capital} % Organization/group
    {Kingston} % Location
    {Apr. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Techstack: HTML, JavaScript, CSS, Bootstrap, jQuery, PHP}
        \item {Resolved website bugs and improved Google Lighthouse score by optimizing images, and removing repeated code, and removing unused CSS.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Developer} % Affiliation/role
    {Queen’s Tech \& Media Association} % Organization/group
    {Kingston} % Location
    {Apr. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Techstack: JavaScript, React.js, Node.js, Express.js, Stripe, Firebase, Bootstrap}
        \item {Developed Pronto a rental marketplace web app for students.}
        \item {Responsible for CRUD system for managing user’s posts, user log-in and authentication, refund capability, a custom live messaging component, and a Stripe API to handle secure transactions between users of the application.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Algorithm Developer} % Affiliation/role
    {Queen's University Algorithmic Network \& Trading Team} % Organization/group
    {Kingston} % Location
    {Sep. 2020 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Techstack: Python, NumPy, pandas, scikit-learn}
        \item {Created forex trading algorithm which was evaluated and trained on the Quant Connect Platform.}
        \item {Used statistical models such as ARIMA to make predictions based on correlation between forex markets and commodities.}
        \item {The trading algorithm was able to make a profit of \$90,000, or 1000\% from an initial investment of \$10,000.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AI Design Team Member} % Affiliation/role
    {QMIND} % Organization/group
    {Kingston} % Location
    {Sep. 2019 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Techstack: Python, TensorFlow, NumPy, pandas, Flask, React.js, JavaScript, Material UI}
        \item {Created an all-in-one Python package for recommender systems and uses a combination of deep, mixed, and matrix-based systems.}
        \item {Presented the package at CUCAI – Canada’s largest undergraduate AI conference.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Teacher's Assistant} % Affiliation/role
    {Pickering High School} % Organization/group
    {Ajax} % Location
    {Sep. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Taught Java, and concepts such as Data Structures and Object-Oriented Programming to over 25 students during my Grade 12 year.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
