%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {Course Central (Course Selection App) - 2021} % Organization/group
    {\href{https://coursecentral.ca/}{\underline{View Project}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Progressive Web and Android app built with Next.js and Java for students to see a course's historical GPA, enrollment data, and leave reviews.}
        \item {Used Selenium Python web scrapers and Deno to collect, aggregate, and then upload the data of over \textbf{850 courses} to MongoDB.}
        \item {Used by over \textbf{1600 students}, with \textbf{11,000+ page views} (according to Firebase Analytics and Authentication).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {Forex Trading Algorithm - 2020} % Organization/group
    {\href{https://github.com/KnlnKS/Forex-Price-Predictor-Quantconnect}{\underline{View Project}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created Python forex trading algorithm which was evaluated and trained on the Quant Connect Platform.}
        \item {Used ARIMA model from statsmodels library to place orders and sells based on correlation between forex markets and commodities.}
        \item {Preprocessed, graphed, and analyzed \textbf{4 years of market data} using Jupyter notebooks, pandas, and Mathplotlib.}
        \item {The trading algorithm was able to make a \textbf{profit of \$90,000} from an initial investment of \$10,000 over the course of 4 months.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {Infinity \& Beyond (Android Game) - 2019} % Organization/group
    {\href{https://play.google.com/store/apps/details?id=com.KKSGames.InifintyandBeyond}{\underline{View Project}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Android arcade game made with Unity and C\#. With assets made with Adobe Photoshop and Adobe Illustrator.}
        \item {Currently sits at a \textbf{4.9 star} rating on the Google Play Store.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
